Stressing Bank Profitability for Interest Rate Risk$^*$ \\ \vspace{0.5cm} Preliminary and Incomplete \vspace{0.5cm}

### 2013-09-08 LATEX/beg.draft.2013.tex
inserted table with Rossi test
added PLS and to Test Table added Figure to paper showing forecasts added table with rolling RMSEs

Our findings have implications beyond the study of net interest margins. Scenario-based stress tests have been used across the world to rebuild confidence in the banking sector in periods of crises. Yet, they are predicated on the assumption that different scenarios for the evolution of the macroeconomy have sufficiently different implications for the evolution of key balance sheet items.  Yet, an array of time series methods found by others to be near the frontier of efficiency produces projections conditional on radically different scenarios for yields that statistically indistinguishable.

@@

\newpage
{\normalsize \clearpage
\begin{sidewaystable}
\center
\caption{RMSE for baseline specifications} \label{table_rmse_baseline}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|}
\hline
&Step 1 &Step 2 &Step 3 &Step 4 &Step 5 &Step 6 &Step 7 &Step 8 &Step 9 &Step 10\\
\hline
1. Simple Forecast Combination             &0.107&0.133&0.148&0.168&0.187&0.202&0.213&0.209&0.216&0.223\\
2. DFM                                                       &0.122&0.148&0.169&0.212&0.247&0.278&0.316&0.340&0.373&0.404\\
3a. DFM with 2nd Step Regression           &0.118&0.167&0.209&0.260&0.308&0.356&0.398&0.433&0.474&0.511\\
3b. DFM with Forecast Combination          &0.112&0.159&0.199&0.247&0.300&0.351&0.399&0.438&0.489&0.535\\
4. Forecast Combination of Observed Factors&0.118&0.169&0.216&0.273&0.336&0.399&0.456&0.509&0.567&0.622\\
5. VAR on Observed Factors                 &0.166&0.209&0.263&0.302&0.342&0.375&0.380&0.430&0.451&0.499\\
6. No-Change Forecast                      &0.107&0.138&0.154&0.181&0.206&0.228&0.244&0.248&0.271&0.293\\
\hline
\end{tabular}
\end{sidewaystable}
}

\newpage
{\normalsize \clearpage
\begin{sidewaystable}
\caption{RMSEs for models that include the share of asset of the shadow banking sector. Estimation sample: 1989Q2-2008Q2} \label{table_rmse_competition}
\center
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|}
\hline
&Step 1 &Step 2 &Step 3 &Step 4 &Step 5 &Step 6 &Step 7 &Step 8 &Step 9 &Step 10\\
\hline
1. Simple Forecast Combination             &0.110&0.143&0.165&0.192&0.222&0.248&0.267&0.274&0.287&0.300\\
3a. DFM with 2nd Step Regression           &0.121&0.170&0.212&0.262&0.312&0.360&0.403&0.436&0.478&0.515\\
3b. DFM with Forecast Combination          &0.106&0.140&0.165&0.193&0.222&0.248&0.267&0.274&0.287&0.300\\
4. Forecast Combination of Observed Factors&0.109&0.141&0.165&0.193&0.222&0.249&0.267&0.274&0.288&0.300\\
5. VAR on Observed Factors                 &0.344&0.396&0.476&0.494&0.521&0.569&0.631&0.670&0.699&0.718\\
6. No-Change Forecast                      &0.107&0.138&0.154&0.181&0.206&0.228&0.244&0.248&0.271&0.293\\
\hline
\end{tabular}
\end{sidewaystable}
}

\newpage \clearpage
\begin{sidewaystable}
\caption{RMSEs for variants of the simple forecast combination model} \label{table_rmse_combination}
\center
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|}
\hline
&Step 1 &Step 2 &Step 3 &Step 4 &Step 5 &Step 6 &Step 7 &Step 8 &Step 9 &Step 10\\
\hline
All yields              &0.107&0.133&0.148&0.168&0.187&0.202&0.213&0.209&0.216&0.223\\
Observed Factors        &0.118&0.169&0.216&0.273&0.336&0.399&0.456&0.509&0.567&0.622\\
Smoothed Factors        &0.112&0.159&0.199&0.247&0.300&0.351&0.399&0.438&0.489&0.535\\
3-month, 2-year, 10-year&0.105&0.130&0.141&0.160&0.178&0.197&0.202&0.198&0.209&0.217\\
3-month, 10-year        &0.105&0.129&0.144&0.159&0.179&0.196&0.200&0.200&0.209&0.217\\
\hline
\end{tabular}
\end{sidewaystable}

@@

>>>>

Our findings have implications beyond the study of net interest margins. Scenario-based stress tests have been used across the world to boost confidence in the banking sector in periods of crises. Yet, they are predicated on the assumption that different scenarios for the evolution of the macroeconomy have sufficiently different implications for the evolution of key balance sheet items.  Yet, an array of time series methods found by others to be near the frontier of efficiency produces projections conditional on radically different scenarios for yields that statistically indistinguishable.

@@

\newpage
{\normalsize \clearpage
\begin{sidewaystable}
\center
\caption{RMSE for baseline specifications -- Recursive Estimation Windows} \label{table_rmse_baseline}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|}
\hline
&Step 1 &Step 2 &Step 3 &Step 4 &Step 5 &Step 6 &Step 7 &Step 8 &Step 9 &Step 10\\
\hline
1. Simple Forecast Combination             &0.107&0.133&0.148&0.168&0.187&0.202&0.213&0.209&0.216&0.223\\
2. DFM                                                       &0.122&0.148&0.169&0.212&0.247&0.278&0.316&0.340&0.373&0.404\\
3a. DFM with 2nd Step Regression           &0.118&0.167&0.209&0.260&0.308&0.356&0.398&0.433&0.474&0.511\\
3b. DFM with Forecast Combination          &0.112&0.159&0.199&0.247&0.300&0.351&0.399&0.438&0.489&0.535\\
4. Forecast Combination of Observed Factors&0.118&0.169&0.216&0.273&0.336&0.399&0.456&0.509&0.567&0.622\\
5. VAR on Observed Factors                 &0.166&0.209&0.263&0.302&0.342&0.375&0.380&0.430&0.451&0.499\\
6. No-Change Forecast                      &0.107&0.138&0.154&0.181&0.206&0.228&0.244&0.248&0.271&0.293\\
\hline
\end{tabular}
\end{sidewaystable}
}

\begin{sidewaystable}       
\caption{RMSE for baseline specifications -- Rolling Estimation Windows} \label{table_rmse_baseline}                                                                              
\center                                                                                           
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|}                                                          
\hline                                                                                            
&Step 1 &Step 2 &Step 3 &Step 4 &Step 5 &Step 6 &Step 7 &Step 8 &Step 9 &Step 10\\                
\hline                                                                                            
1. F. Combination - Yields          &0.113&0.135&0.150&0.165&0.180&0.190&0.203&0.205&0.205&0.210\\
3a. DFM with 2nd Step Reg.          &0.111&0.146&0.174&0.209&0.244&0.279&0.307&0.333&0.369&0.403\\
3b. DFM with F. Combination         &0.113&0.168&0.211&0.263&0.324&0.372&0.419&0.461&0.508&0.547\\
4. PCR                              &0.118&0.167&0.208&0.259&0.307&0.355&0.397&0.432&0.472&0.508\\
5. PLS                              &0.111&0.147&0.173&0.195&0.215&0.234&0.251&0.268&0.300&0.333\\
6. F. Combination - Observed Factors&0.113&0.155&0.189&0.235&0.293&0.347&0.398&0.452&0.510&0.564\\
7. VAR on Observed Factors          &0.871&0.906&0.562&1.040&1.094&0.786&0.872&0.459&0.409&0.468\\
8. No-Change Forecast               &0.107&0.138&0.154&0.181&0.206&0.228&0.244&0.248&0.271&0.293\\
\hline                                                                                            
\end{tabular}                                                                                     
\end{sidewaystable}

\normalsize \clearpage
\renewcommand{\baselinestretch}{1} 
\begin{table}  
\caption{Decomposing the Relative Performance of 1-Step Ahead Forecasts}                                                        
\center                                                                
\begin{tabular}{|l|l|c|c|}                                             
\hline                                                                 
&&m = 4&m=12 \\                                                        
\hline                                                                 
1. F. Combination - Yields          & DMW&\multicolumn{2}{|c|}{1.170}\\
\hline                                                                 
& $\Gamma_P^{(A)}$&11.153*&2.477\\                                     
& $\Gamma_P^{(B)}$&3.056*&3.056*\\                                     
& $\Gamma_P^{(U)}$&0.490&0.490\\                                       
\hline                                                                 
3a. DFM with 2nd Step Reg.          & DMW&\multicolumn{2}{|c|}{0.478}\\
\hline                                                                 
& $\Gamma_P^{(A)}$&7.684&3.727\\                                       
& $\Gamma_P^{(B)}$&-0.806&-0.806\\                                     
& $\Gamma_P^{(U)}$&1.146&1.146\\                                       
\hline                                                                 
3b. DFM with F. Combination         & DMW&\multicolumn{2}{|c|}{0.773}\\
\hline                                                                 
& $\Gamma_P^{(A)}$&6.841&2.441\\                                       
& $\Gamma_P^{(B)}$&2.923*&2.923*\\                                     
& $\Gamma_P^{(U)}$&0.769&0.769\\                                       
\hline                                                                 
4. PCR                              & DMW&\multicolumn{2}{|c|}{1.040}\\
\hline                                                                 
& $\Gamma_P^{(A)}$&8.324&3.873\\                                       
& $\Gamma_P^{(B)}$&-0.059&-0.059\\                                     
& $\Gamma_P^{(U)}$&1.445&1.445\\                                       
\hline                                                                 
5. PLS                              & DMW&\multicolumn{2}{|c|}{0.638}\\
\hline                                                                 
& $\Gamma_P^{(A)}$&7.105&3.710\\                                       
& $\Gamma_P^{(B)}$&-0.630&-0.630\\                                     
& $\Gamma_P^{(U)}$&1.209&1.209\\                                       
\hline                                                                 
6. F. Combination - Observed Factors& DMW&\multicolumn{2}{|c|}{0.855}\\
\hline                                                                 
& $\Gamma_P^{(A)}$&6.518&2.863\\                                       
& $\Gamma_P^{(B)}$&-2.711*&-2.711*\\                                   
& $\Gamma_P^{(U)}$&2.025*&2.025*\\                                     
\hline                                                                 
7. VAR on Observed Factors          & DMW&\multicolumn{2}{|c|}{1.250}\\
\hline                                                                 
& $\Gamma_P^{(A)}$&9.040&2.208\\                                       
& $\Gamma_P^{(B)}$&1.836&1.836\\                                       
& $\Gamma_P^{(U)}$&-1.249&-1.249\\                                     
\hline                                                                 
\end{tabular}                                                          
\end{table}

\clearpage
\renewcommand{\baselinestretch}{1.5} \normalsize

\begin{sidewaystable}
\caption{RMSEs for models that include the share of asset of the shadow banking sector. Estimation sample: 1989Q2-2008Q2} \label{table_rmse_competition}
\center
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|}
\hline
&Step 1 &Step 2 &Step 3 &Step 4 &Step 5 &Step 6 &Step 7 &Step 8 &Step 9 &Step 10\\
\hline
1. Simple Forecast Combination             &0.110&0.143&0.165&0.192&0.222&0.248&0.267&0.274&0.287&0.300\\
3a. DFM with 2nd Step Regression           &0.121&0.170&0.212&0.262&0.312&0.360&0.403&0.436&0.478&0.515\\
3b. DFM with Forecast Combination          &0.106&0.140&0.165&0.193&0.222&0.248&0.267&0.274&0.287&0.300\\
4. Forecast Combination of Observed Factors&0.109&0.141&0.165&0.193&0.222&0.249&0.267&0.274&0.288&0.300\\
5. VAR on Observed Factors                 &0.344&0.396&0.476&0.494&0.521&0.569&0.631&0.670&0.699&0.718\\
6. No-Change Forecast                      &0.107&0.138&0.154&0.181&0.206&0.228&0.244&0.248&0.271&0.293\\
\hline
\end{tabular}
\end{sidewaystable}

\clearpage
\begin{sidewaystable}
\caption{RMSEs for variants of the simple forecast combination model} \label{table_rmse_combination}
\center
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|}
\hline
&Step 1 &Step 2 &Step 3 &Step 4 &Step 5 &Step 6 &Step 7 &Step 8 &Step 9 &Step 10\\
\hline
All yields              &0.107&0.133&0.148&0.168&0.187&0.202&0.213&0.209&0.216&0.223\\
Observed Factors        &0.118&0.169&0.216&0.273&0.336&0.399&0.456&0.509&0.567&0.622\\
Smoothed Factors        &0.112&0.159&0.199&0.247&0.300&0.351&0.399&0.438&0.489&0.535\\
3-month, 2-year, 10-year&0.105&0.130&0.141&0.160&0.178&0.197&0.202&0.198&0.209&0.217\\
3-month, 10-year        &0.105&0.129&0.144&0.159&0.179&0.196&0.200&0.200&0.209&0.217\\
\hline
\end{tabular}
\end{sidewaystable}

@@

\clearpage
\begin{figure}
\flushleft
\caption{Pseudo-Out-of-Sample Forecasts} \label{figure_forecasts}
 \includegraphics[scale=0.85]{figure_forecasts.ps}
\end{figure}
